{\sc Kalashnikov}: Fully Automatic Loop Free Program Synthesis by Bounded Model Checking

### 2013-09-20 paper/paper.tex
Cleaned up description of generalization

The only wrinkle here is that sometimes a program we synthesize will contain
constants.  If we have synthesized a program for a machine with $k$-bit words,
the constants in the program will be $k$ bits wide.  To generalize the program
to a $n$-bit machine (with $n > k$), we need some way of deriving $n$-bit
wide numbers from $k$-bit ones.  We have several strategies for this and
just try each in turn.  To generalize a number $x$ we use the following
rules:

>>>>

The only wrinkle here is that sometimes a program we synthesize will contain
constants.  If we have synthesized a program for a machine with $k$-bit words,
the constants in the program will be $k$ bits wide.  To generalize the program
to a $n$-bit machine (with $n > k$), we need some way of deriving $n$-bit
wide numbers from $k$-bit ones.  We have several strategies for this and
just try each in turn.  In the following, a subscript $n$ on a value means that
the value is an $n$-bit word.  The dot operator $a_l \cdot b_m$ denotes
concatenation, resulting in an $(l+m)$-bit wide word.  A superscript on a value
means duplication, so $a_l^m$ means concatenating together $m$ copies of the $l$-bit
word $a$, resulting in an $(lm)$-bit wide word.

To generalize a number $x$ we use the following rules:
